---
title: "polygons: Flexible functions for computing polygons coordinates in R"
output: github_document
---

[![Travis build status](https://travis-ci.org/USCbiostats/polygons.svg?branch=master)](https://travis-ci.org/USCbiostats/polygons) [![Build status](https://ci.appveyor.com/api/projects/status/1s03nj397tbkrc56?svg=true)](https://ci.appveyor.com/project/gvegayon/polygons)


<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%"
)
```

The goal of polygons is to ...

## Example

Here is a basic example of a very controversial type of plot but that anyway can be useful in some situations... the pie chart!:

```{r example, fig.width=8, fig.height=6}
library(polygons)

oldpar <- par(mfrow=c(1,2), mai=rep(0, 4))
piechart(1:10, density=(1:10)^2/2, slice.off = (1:10)/30, doughnut = .5,
  radius = sqrt(10:1),
  # Here we are setting random labels...
  labels=sapply(1:10, function(x) paste(sample(letters, x, TRUE), collapse=""))
  )

vals <- c(1,2,3,10)

# Outer (includes labels)
piechart(vals, col=grDevices::blues9[5:8], border=NA, doughnut = .5,
    radius=.75, labels=vals, init.angle = 315, last.angle = 270)

# Middle
piechart(vals, col=grDevices::blues9[3:6], border=NA, doughnut = .3,
    radius=.5, add=TRUE, init.angle = 315, last.angle = 270)

# Inner
piechart(vals, col=grDevices::blues9[1:4], border="gray", doughnut = .1,
    radius=.3, add=TRUE, init.angle = 315, last.angle = 270)

par(oldpar)
```


Nice n-sided polygons with the `npolygon` function:

```{r example2, out.width=600, out.height=600, fig.width=6, fig.height=6}
oldpar <- par(no.readonly = TRUE)

par(xpd = NA, mfrow = c(3, 3), mai = rep(0, 4))
for (n in c(2, 3, 4, 5, 6, 8, 12, 20, 50)) {

  plot.new()
  plot.window(c(-1.25,1.25), c(-1.25,1.25))

  # We loop through this sequence to generate a nice decay of colors
  for (i in seq(1, .0005, length.out = 200)) {
    col <- adjustcolor("tomato", alpha.f = i)
    
    # After calling npolygon, we call polygon to draw it
    polygon(npolygon(x=(i-1)/4, y = (i-1)/4, r = i, d = i-1, n = n),
            col = NA, border=col)
  }

  mtext(sprintf("n = %i", n), side = 1, line = -3)
}

par(oldpar)
```

Color decayed segments with `segments_gradient` and a nice colorkey with `colorkey`

```{r color-segments, fig.width=7, fig.height=7}
set.seed(2315231)
n <- 1e4
x <- cbind(cumsum(rnorm(n, sd=.1)), cumsum(rnorm(n, sd=.05)))

plot(x, type="n", main="A random walk")
segments_gradient(x, col = colorRamp2(viridis::viridis(2)))


# And nice color keys
colorkey(.5,0,1,.1, cols = viridis::viridis(2), tick.range = c(1, n),
         main = "Step", tick.args = list(cex=.7))
```

A faster implementation of `colorRamp`, `colorRamp2` which allows specifying threshold levels (mixing levels) for the colors

```{r color-ramp}
myf  <- colorRamp2(c("black", "steelblue"))
myf2 <- colorRamp2(c("black", "steelblue"), thresholds=c(0, .7))

plot.new()
plot.window(xlim = c(0,2), ylim = c(1, 11))

rect(
  xleft   = 0,
  xright  = 1,
  ybottom = 1:10,
  ytop    = 2:11,
  col = rgb(myf((1:10)/10), maxColorValue = 255)
  )
rect(
  xleft   = 1,
  xright  = 2,
  ybottom = 1:10,
  ytop    = 2:11,
  col = rgb(myf2((1:10)/10), maxColorValue = 255)
)
```

